---
title: "Dependent Sampling"
section: "Bayesian Statistics"
author: "Chaichontat Sriworarat"
date: 2019-10-15
tags: ["bayesian statistics"]
include-before:
  - '$\newcommand{\summ}{\sum_{i=1}^n}$'
  - '$\newcommand{\prodd}{\prod_{i=1}^n}$'
  - '$\newcommand{\xdots}{x_1, \dots, x_n}$'
  - '$\newcommand{\expb}[1]{\exp\left\{#1\right\}}$'
  - '$\newcommand{\pp}[1]{\left(#1\right)}$'
  - '$\newcommand{\b}[1]{\mathbf{#1}}$'
  - '$\newcommand{\bs}[1]{\boldsymbol{#1}}$'
---
```{r}
library(JuliaCall)
julia_setup("/Applications/Julia-1.2.app/Contents/Resources/julia/bin/")
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_engines$set(julia = JuliaCall::eng_juliacall)
```
# Why dependent sampling?

# Gibbs Sampling

* Gibbs sampling is used to approximate the joint distribution when we have the full conditional distribution of all parameters.
  * In the normal model, there are two parameters, $\mu$ and $\sigma^2$.
  * We can estimate $p(\mu, \sigma^2 \mid \xdots)$ using $p(\mu\mid\sigma^2,\xdots)$ and $p(\sigma^2\mid\mu,\xdots)$.
  * This is like turning a multiparameter model into a single parameter model as each full conditional is the same thing as the posterior of a single parameter model.
  
```{julia}
using Distributions, StatsPlots, Statistics
gr()

function gibbs_normal(iter=5000)
    # Prior Values
    σ²₀ = 0.01; μ₀ = 1.9; τ²₀ = 0.95^2; n₀ = 1;
    
    # Data
    x = [1.64, 1.70, 1.72, 1.74, 1.82, 1.82, 1.82, 1.90, 2.08]
    x̄ = mean(x); s² = var(x); n = length(x)
    
    # Initialization
    ϕ = zeros(iter, 2)
    ϕ[1, 1] = x̄
    ϕ[1, 2] = s²
    α = (n + n₀) / 2
    
    for i in 2:iter
        
        # Sample for μ
        σ² = ϕ[i-1, 2]
        μₙ = (n*x̄/σ² + μ₀/τ²₀) / (n/σ² + 1/τ²₀)
        τ²ₙ = (n/σ² + 1/τ²₀)^-1
        ϕ[i, 1] = rand(Normal(μₙ, sqrt(τ²ₙ)))
        
        # Sample for σ²
        μ = ϕ[i, 1]
        β = ((n-1)*s² + n₀*σ²₀ + n*(x̄-μ)^2) / 2
        ϕ[i, 2] = rand(InverseGamma(α, β))
    end
    
    return ϕ
end

t = gibbs_normal()
```

```{r}
JuliaCall::julia_command("scatter(t[100:end,1], 1 ./ t[100:end,2], alpha=0.2, markerstrokewidth=0)")
```

# Metropolis Algorithm
